---
output: github_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(sf)
library(hvspkg)
```

# hvspkg

An R package for assessing heat vulnerability across Spanish municipalities
by integrating satellite-derived land surface temperature (LST), vegetation
indicators (NDVI), and demographic data.

## Installation

```{r eval=FALSE}
devtools::install_github("cczablan1/hvspkg", ref = "truedata", build_vignettes = TRUE)
```

## Usage

```{r}
library(hvspkg)

# Step 1 — Join population to municipalities
muni <- join_population_to_municipalities(
  example_municipalities,
  example_population
)

# Step 2 — Create hvi_municipalities object
hvi_muni <- new_hvi_municipalities(muni)
print(hvi_muni)
summary(hvi_muni)
```

```{r eval=FALSE}
# Step 3 — Extract raster statistics (requires TIF files)
hvi_muni <- extract_raster_to_municipalities(
  hvi_muni,
  lst_path  = "data-raw/spain_LST_2021.tif",
  ndvi_path = "data-raw/spain_NDVI_mean_2021.tif"
)
```

```{r echo=FALSE}
# Simulated for README build
set.seed(42)
hvi_muni$LST_mean  <- runif(nrow(hvi_muni), 25, 45)
hvi_muni$NDVI_mean <- runif(nrow(hvi_muni), 0.1, 0.6)
```

```{r}
# Step 4 — Compute and plot the Heat Vulnerability Index
hvi <- compute_hvi_score(hvi_muni)
print(hvi)
plot(hvi)
```

## Data sources

- Municipality boundaries: IGN via ArcGIS Living Atlas
- Population by age and sex: INE
- LST: MODIS MOD11A2.061 (NASA LP DAAC)
- NDVI: MODIS MOD13Q1.061 (NASA LP DAAC)
- Province codes: INE